Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-11 write-ups/PLDI/paper.tex
More semantic differences.

\ADComment{TODO: explain why we have thread 0 transmit its state, and transmitting only annotated variables.}

>>>>

Recall from the semantics of $\offerfork$ that newly forked workgroups
inherit the variable valuation associated with thread 0 of the forking
workgroup, but only for $\transmit$-annotated variables.  Alternative
choices here would be to have forked workgroups inherit values for
\emph{all} variables from the forking workgroup, and to have thread
$i$ in the forking workgroup provide the valuation for thread $i$ in
each spawned workgroup, rather than having thread 0 transmit the
valuation to all new threads.

\ADComment{TODO: justify our choice: uniform variables and efficiency.}
